---
title: "introduct"
author: Jeng_Long Sheu
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduct}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Package Description

`fars` package can pickup some data and plot graphic whit you input arguments from FARS data.FARS is a database which had build by [National Highway Traffic Safety Administration](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars).

[FARS](https://en.wikipedia.org/wiki/Fatality_Analysis_Reporting_System) is a
nationwide census, providing the American public yearly data, regarding fatal
injuries suffered in motor vehicle traffic crashes.


## Require Packages

```{r}
library(fars) 
library(maps) 
```


## Included data

Data files included within the package:

```{r}
list.files(system.file("extdata", package = "fars"))
```


## Package Functions

### Function `make_filename`

This function make .csv file names related to the argument year.

```{r}
yr <- 2013
make_filename(yr)
```

### Function `fars_read_years`

This function takes a vector of years and produces a list of tibbles,where each tibble is that year's FARS file year and MONTH observations.

```{r}
yr <- 2015
fars_read_years(yr)
```


### Function `fars_summarize_years`

This function summarizes yearly accidents data, by month.

```{r}
#plot(fars_summarize_years(2015))
#fars_summarize_years(c(2015, 2014))
```

### Function `fars_map_state`

This function provide a plot with a state map including the accidents location by year.

```{r}
fars_map_state(35, 2013)
```
